Lay Perceptions of Crowd-Scientific Findings: The Risks of Variability and Lack of Consensus

### 2021-10-11 index.Rmd
repositioned the speaker note
fixed mistake notes

@@

First, I'll share a brief open science statement and links to all the available materials. Then, I'll define crowd science.s
---
class: inverse, middle, center
name: openscience

@@

In 1833, Denison Olmsted used letter correspondence to recruit citizen scientists to help document a meteor shower. This led to a detailed documentation of the great meteor shower and the birth of the citizen-science movement (highly inclusive, used for data collection.
---
class: inverse, center, middle
name: crowddata

@@

??? 3 papers published in 2021, one looking at variability in the analysis of replications, another one at opinions about different social policies, and one OBHDP looking at the effects of scientists’ gender and professional status on verbosity during group meetings. Two papers in 2020, one looking at variability in the analysis of fmri (neuroimaging datasets), another in applied microeconomics. One paper from 2019 that evaluated the extent to which clinical psychologists analyzing the same experience sampling data come to different conclusions about symptoms to target for treatment. And one really famous study in 2018, that looked at discrimination against darker skin toned soccer players, and arguably started the recent crowd science movement in behavioral science.

>>>>

First, I'll share a brief open science statement and links to all the available materials. Then, I'll define crowd science.

@@

---
class: inverse, middle, center
name: openscience

@@

In 1833, Denison Olmsted used letter correspondence to recruit citizen scientists to help document a meteor shower. This led to a detailed documentation of the great meteor shower and the birth of the citizen-science movement (highly inclusive, used for data collection. In terms of the two dimensions we just discussed, this project can be categorized as highly inclusive - because it sourced citizens - and as used in the stage of data collection. 
---
class: inverse, center, middle
name: crowddata

@@

3 papers published in 2021, one looking at variability in the analysis of replications, another one at opinions about different social policies, and one OBHDP looking at the effects of scientists’ gender and professional status on verbosity during group meetings. Two papers in 2020, one looking at variability in the analysis of fmri (neuroimaging datasets), another in applied microeconomics. One paper from 2019 that evaluated the extent to which clinical psychologists analyzing the same experience sampling data come to different conclusions about symptoms to target for treatment. And one really famous study in 2018, that looked at discrimination against darker skin toned soccer players, and arguably started the recent crowd science movement in behavioral science.
